Mirror, mirror on the wall. Which's the best match of them all?

### 2023-12-15 PNAS/index.Rnw
Updates

\firstpage[8]{6}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

\dropcap{I}n forensic \ac{evaluations}, a single conclusion often \ac{relies} on  many comparisons, either implicitly or explicitly.
Multiple comparisons arise persistently when developing statistical methods to address scientific problems \citep{benjaminiControllingFalseDiscovery1995}, and can significantly increase the probability of false "discoveries".  Yet, this potentially significant issue is often ignored.  \ac{Now that vast databases and efficient algorithms are routinely used in forensic evaluations to find "matches" to crime scene items, the problems of close non-matches\citep{pcast}, and of the erosion of confidence due to multiple comparisons, become critically important.}
%Researchers have been focusing on building up databases to develop algorithms for objective evidence comparisons.
%\svp{Then, the algorithms facilitate} searches across (vast) databases, reporting the best $N$ matches to a particular piece of evidence.
%This raises the critically important problem of .

>>>>

\firstpage[3]{6}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

\dropcap{I}n forensic \ac{evaluations}, a single conclusion often \ac{relies} on  many comparisons, either implicitly or explicitly.
Multiple comparisons arise persistently when developing statistical methods to address scientific problems \citep{benjaminiControllingFalseDiscovery1995}, and can significantly increase the probability of false "discoveries".  Yet, this potentially significant issue is often ignored.  \ac{Now that vast databases and efficient algorithms are routinely used in forensic evaluations to find "matches" to crime scene items, the problems of close non-matches\citep{pcast} and the erosion of confidence due to multiple comparisons become critically important.}
%Researchers have been focusing on building up databases to develop algorithms for objective evidence comparisons.
%\svp{Then, the algorithms facilitate} searches across (vast) databases, reporting the best $N$ matches to a particular piece of evidence.
%This raises the critically important problem of .
